Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-06 paper/galsize_paper.tex
Added paragraph in Intro describing each section's contents

@@

\section{Relation to Previous Work}
\label{subsec:previous_work}

>>>>

The approach we take is is to forward model the $\rhalf-$halo connection: we generate a Monte Carlo realizations of the model, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples. We describe the dataset and simulations we use in \S\ref{sec:data}, and our forward-modeling methods in \S\ref{sec:model}. All of our primary results appear in \S\ref{sec:results}, and their theoretical interpretation in \S\ref{sec:interpretation}. We contextualize our findings in terms of previous work in \S\ref{sec:previous_work}, and discuss future directions in \S\ref{sec:future}. We conclude the paper with a summary of our principal results in \S\ref{sec:conclusion}.

@@

\section{Relation to Previous Work}
\label{sec:previous_work}
